An Audio-Based 3D Spatial Guidance AR System for Blind Users\thanks{JMC, BB and HS were supported by NIH grant 5R01EY025332 and NIDILRR grant 90RE5024-01-00. We thank Dr. Roberto Manduchi, Dr. Natela Shanidze, Dr. Santani Teng and Dr. Ali Cheraghi for helpful suggestions about the experiments.}

### 2020-06-10 manuscript.tex
Updates from Overleaf

\begin{figure}
\includegraphics[width=5.5cm, keepaspectratio,]{res/img/fig2a.jpg}
\includegraphics[width=6.5cm, keepaspectratio,]{res/img/fig2b.jpg}
\caption{(left) Plot of time (x axis) to find target hotspot location for G (‘o’ symbol) vs. NG  (‘x’ symbol) conditions, with time-out declared after 120 sec. of unsuccessful search. Results are shown for each participant (indicated on the y axis and also using color) and at all 10 target locations. (right) Histogram plot showing the distribution of NG time minus G time. The plot aggregates time differences for all participants over all locations; positive times mean the search was faster with G than with NG.}
\label{fig:res}
\end{figure}

We analyzed the differences between times under G vs.~NG using a
Wilcoxon signed rank test. The resulting p-value is p = 3.8 x 10-8. This
is a highly statistically significant p-value supporting the rejection
of the null hypothesis that the distribution of times under G is the
same as the distribution of times under NG.

>>>>

%%TODO: figure description
%%TODO: split the 4 figures ?
\begin{figure}
\includegraphics[width=5.5cm, height=4.1cm,]{res/img/histNG.png}
\includegraphics[width=6.5cm, keepaspectratio,]{res/img/lines.png}
\includegraphics[width=5.5cm, keepaspectratio,]{res/img/fig2a.jpg}
\includegraphics[width=6.5cm, keepaspectratio,]{res/img/fig2b.jpg}
\caption{
(Upper-left) Histogram of the times to find the hotspots per guidance condition. 
(Upper-right) Line plot showing the average time to find the hotspot ($\pm{ SE}$) per subject and per guidance condition. 
(Bottom-left) Time to find target hotspot location for G (‘o’ symbol) vs. NG  (‘x’ symbol) conditions. The times for each of the 10 hotspots are shown, for each participant (indicated on the y axis and also using color). 
(Bottom-right) Histogram of the differences (paired by hotspot) in time to find the hotspot.}
\label{fig:res}
\end{figure}

We used a Wilcoxon Signed Rank test to compare the differences between G and NG times, paired by hotspot within each participant. The result indicated that participants performed significantly better in the guided condition (med = 14,5) than in the non guided one (med = 120), with T=815, z=5.45, $p < 0.001$, and an effect size of V = 0.86.
